### 2018-11-09 articleSFDS.tex
fin modification partie résultats

%Figure \ref{fig:comparisionDensities1} compares the results obtained (with the help of the \textbf{R} package CaliCo \citep{CaliCo}) 
%for $\eta$, $\mu_t$, $a_r$ and $\sigma_{err}^2$ for each model. In each case, the MCMC chains converge. 
%For the first model, a strong disagreement has appeared between the \textit{prior} and \textit{posterior} densities for $\sigma_{err}^2$. 
%The Maximum A Posteriori (MAP) of $\sigma_{err}^2$'s density, for $\mathcal{M}_1$,
% is around $6500\ W^2$. That makes a standard deviation of $80.6W$ which is too high and has no physical trustworthiness. 
%For $\mathcal{M}_2$, $\mathcal{M}_3$ and $\mathcal{M}_4$ the MAP estimations of $\sigma_{err}^2$'s densities seem to be coherent with physics. The addition of the discrepancy between $\mathcal{M}_1$ and $\mathcal{M}_3$ then between $\mathcal{M}_2$ and $\mathcal{M}_4$ depicts a correlation (an error structure) in $\boldsymbol{y}_e$. When, no code error is applied, the variance from this covariance matrix is added to the variance of the measurement error. \newline

Figure \ref{fig:comparisionDensities1} compares the results obtained with the help of the \textbf{R} package CaliCo \citep{CaliCo}. For each parameter $\eta$, $\mu$, $a_r$ and $\sigma_{err}^2$, the MCMC chains converge. Indeed, good mixing properties are chosen after a visual check. Figure \ref{fig:comparisionDensities1} confronts the \textit{prior} densities with the \textit{posterior} densities. In almost every model, a decrease of the variance is quantifiable which illustrates an improvement on the knowledge of the parameter density. However, the decrease of variance is not equal for every model. Calibration realized with the model $\mathcal{M}_2$ produces \textit{posterior} densities with bigger variances than for the $\mathcal{M}_1$. The replacement of the numerical code by a Gaussian process have added a variance term in the full likelihood which increases the variance \textit{a posteriori}. The same phenomenon is visible from the model $\mathcal{M}_3$ to the model $\mathcal{M}_4$. Calibration with the model $\mathcal{M}_1$ also brings a strong disagreement in the estimation of the \textit{posterior} density of $\sigma_{err}^2$. The Maximum A Posteriori (MAP) of $sigma_{err}^2$ is $6500\ W^2$ which makes a standard deviation of $80.6\ W$. This value is too high and has no physical trustworthiness. From calibration with the model $\mathcal{M}_1$ to the model $\mathcal{M}_3$, the \textit{posterior} density of $\sigma_{err}^2$ has been corrected in accordance with the prior distribution and the physical sense. It does not mean that calibration with the model $\mathcal{M}_1$ is incorrect, it only means that this model miss a substantial variance term. This term is the discrepancy and if one wants to be consistent with physics, one should consider the model $\mathcal{M}_3$ in this case.\newline

@@

The use of a Gaussian process as a surrogate of the code (in the models $\mathcal{M}_2$ and $\mathcal{M}_4$) has to be manipulated with caution. Most of industrial codes are time consuming and the use of small DOE is required. However, if the surrogate does not represent well enough the numerical code, calibration will fail to retrieve a physical sense for the parameter. A shift of the \textit{posterior} density compared to the \textit{prior} density appear and calibration cannot be interpreted properly. A criterion can be introduced that can be seen as a recommendation upstream calibration: the $Q2$ of the surrogate has to be higher than $0.8$ to access proper calibration. Even with a $Q2>0.8$, calibration can lead to really wide \textit{posterior} densities which is the case in Figure \ref{fig:comparisionDensities1} for $\mathcal{M}_2$ and $\mathcal{M}_4$. This small decrease of variance \textit{a posteriori} might be unsatisfactory for the industrial company. An improvement of the Gaussian process can be brought by adding a small number of well chosen points in the original DOE. This methodology is a sequential design developed in \citet{damblin2018} and is based on the EGO optimization to find new points regarding further calibration. From the original DOE of $50$ points used to obtain calibrations with $\mathcal{M}_2$ and $\mathcal{M}_4$ in Figure \ref{fig:comparisionDensities1}, $10$ points are appended to the original DOE by using the sequential design. Then calibration is performed on the new Gaussian process emulated with the new DOE and the results are displayed in Figure \ref{fig:calibrationSeq}. \newline

@@

%
%\begin{figure}[htbp!]
%\centering
%    \begin{tikzpicture}
%		\tikzstyle{m1}=[]
%		\node[m1] (N1) at (0,0) {\includegraphics[width=.3\textwidth]{figR/corrPlot.pdf}};
%		\node[m1] (N2) at (-2,1) {$\eta$};
%		\node[m1] (N3) at (-1,2) {$\eta$};
%		\node[m1] (N4) at (0,2) {$\mu_t$};
%		\node[m1] (N5) at (-1,0) {$\mu_t$};
%		\node[m1] (N6) at (1,2) {$a_r$};
%		\node[m1] (N6) at (0,-1) {$a_r$};
%    \end{tikzpicture}
%    
%\caption{Correlation representation between the parameters}
%\label{fig:corrPlot}
%\end{figure}

%This disagreement becomes even more important with the second model in which the variance of the \textit{posterior} density is too high to make sense for doing any parameter estimation. However in the third and fourth model, the disagreement has vanished. The maximum \textit{a posteriori} of the measurement error variance even seems to be the coherent regarding \textit{prior} densities.\newline
%  
%In the two first models, the measurement errors are much bigger than expected \textit{a priori}. As a matter of fact, a code error is included and estimated in the $\epsilon's$ without knowing it. Figure \ref{fig:comparisionDensities1} illustrates this phenomenon because, when the discrepancy is modeled, the whole model gets more physical sense. In the two first cases, the maximum \textit{a posteriori} of $\sigma_{err}^2$ is about respectively $1000$ and $6000$. That makes a standard deviation of about $31.62W$ and $77.45W$. Such a measurement error does not physically makes sense.\newline

@@

Figure \ref{fig:comparisionDensities2} illustrates the estimation of the parameters from the discrepancy term.
As expected, learning from data has improved our \textit{prior} belief by decreasing the \textit{prior} uncertainty of the parameters. 
It shows that in both cases (with and without surrogate) that the convergence seems to be reached at some point. \newline
%The fact that the values may slightly differ from each other is not an issue because the models are intrinsically different. \newpage

@@

& $\mathcal{M}_1$ & $\mathcal{M}_2$ & $\mathcal{M}_3$ & $\mathcal{M}_4$ & $\mathcal{M}_2'$&  $\mathcal{M}_4'$ \\
\hline
\hline
coverage rate at 90\% (in \%) & 91 & 44 & 85 & NAN & 71 & NAN \\
\hline
RMSE of the instantaneous power ($W$) & 5.103 & 21.79 & 4.56 & NAN & 10.94 & NAN \\
\end{tabular}
\end{table}

The coverage rates for $\mathcal{M}_1$ and $\mathcal{M}_3$ corresponds to the chosen credibility level.
However for $\mathcal{M}_2$ and $\mathcal{M}_4$ 
the coverage rates are below this level. As expected the coverage rates of $\mathcal{M}_2'$ and $\mathcal{M}_4'$

This was expected since the coverage rates for the code emulation displayed in Table \ref{tab:comparisonPG} were below the fixed credibility level
especially when the DOE had only $50$ points. We recall that these coverage rates only account for the surrogate error and not for the uncertainty
on $\boldsymbol{\theta}$.
We also notice that the predictive power increases when the discrepancy is added. \newline

%The cover rate seems to be quite good for $\mathcal{M}_1$, $\mathcal{M}_3$ and $\mathcal{M}_4$. However, for $\mathcal{M}_2$, the rate is lower because the Gaussian process which emulates the code had difficulties to reach every points of the outputs of the code (which is due to high fluctuations). The comparison of the RMSE of the instantaneous power leads to a similar conclusion. The different models $\mathcal{M}_1$, $\mathcal{M}_3$ and $\mathcal{M}_4$ reach a good estimation. Even for the integrated energy, the results are similar. It is interesting to note that the discrepancy did improve a little the initial computational code (from $\mathcal{M}_1$ to $\mathcal{M}_3$). When the surrogate only is used, the results are not satisfactory ($\mathcal{M}_2$). However when the discrepancy is added to the surrogate, the prediction is a lot better ($\mathcal{M}_4$).\newline

@@

%Overall, the model $\mathcal{M}_4$ has better results than the others. This conclusion can be explained by the fact that the surrogate tries to smooth the response of the code, and each time the surrogate is called, it reproduces an error. The discrepancy trends to counter this error. Very surprisingly, $\mathcal{M}_4$ does a better job than $\mathcal{M}_3$ (although the latter can freely access as many runs of the code as required). This might be explained because the Gaussian process used for simulating the discrepancy has a better matching association with other Gaussian processes. The code encounters a lot of fluctuations and as we can see Table \ref{tab:comparison}, the discrepancy has more trouble to estimate its code error (from $\mathcal{M}_1$ to $\mathcal{M}_3$) than the one from the surrogate (from $\mathcal{M}_1$ to $\mathcal{M}_3$). \newline

%The interest of calibration is to assess, in a better way, the error of a quantity of interest. 
%For example, Figure \ref{fig:ParamError}, we have introduced the $90\%$ \textit{priori} credibility interval. 
%After running calibration for each model, the results illustrate a decrease on this credibility interval (Figure \ref{fig:interestCalibration}).
%In the cases of $\mathcal{M}_3$ and $\mathcal{M}_4$, the \textit{posteriori} credibility interval  is mainly represented by the discrepancy .

%\begin{figure}[htbp!]
%\begin{center}
%   \begin{tabular}{cc}
%   \rotatebox{90}{ \hspace{4em} \small density}
% 	&  \includegraphics[width=.35\textwidth]{figR/model1/densityAr.pdf}\\
%     \end{tabular}
%    \begin{tabular}{cccccc}
%    & A \textit{priori} & $\mathcal{M}_1$ & $\mathcal{M}_2$ & $\mathcal{M}_3$
%    & $\mathcal{M}_4$\\
%	\rotatebox{90}{ \hspace{0.5em} \small Power in $W$}
%    & \includegraphics[width=.17\textwidth]{figR/credInterPrior.pdf}
%    & \includegraphics[width=.17\textwidth]{figR/model1Output.pdf}
%    & \includegraphics[width=.17\textwidth]{figR/model2Output.pdf}
%   & \includegraphics[width=.17\textwidth]{figR/model3Output.pdf}
%    & \includegraphics[width=.17\textwidth]{figR/model4Output.pdf}
%    \\
%    & \multicolumn{5}{c}{Time in hour}\\
%	&&\\
%  \end{tabular}   
%\caption{The $90\%$ credibility interval a priori is showed on the first panel against the $90\%$ credibility interval a posteriori for each models.}
%\label{fig:interestCalibration}
%\end{center}
%\end{figure}

>>>>

Figure \ref{fig:comparisionDensities1} compares the results obtained with the help of the \textbf{R} package CaliCo \citep{CaliCo}. For each parameter $\eta$, $\mu$, $a_r$ and $\sigma_{err}^2$, the MCMC chains converge. Indeed, good mixing properties are chosen after a visual check. Figure \ref{fig:comparisionDensities1} confronts the \textit{prior} densities with the \textit{posterior} densities. In almost every model, a decrease of the variance is quantifiable which illustrates an improvement on the knowledge of the parameter density. However, the decrease of variance is not equal for every model. Calibration realized with the model $\mathcal{M}_2$ produces \textit{posterior} densities with bigger variances than for $\mathcal{M}_1$. The replacement of the numerical code by a Gaussian process have added a variance term in the full likelihood which increases the variance \textit{a posteriori}. The same phenomenon is visible from the model $\mathcal{M}_3$ to the model $\mathcal{M}_4$. Calibration with the model $\mathcal{M}_1$ also brings a strong disagreement in the estimation of the \textit{posterior} density of $\sigma_{err}^2$. The Maximum A Posteriori (MAP) of $\sigma_{err}^2$ is $6500\ W^2$ which makes a standard deviation of $80.6\ W$. This value is too high and has no physical trustworthiness. From calibration with the model $\mathcal{M}_1$ to the model $\mathcal{M}_3$, the \textit{posterior} density of $\sigma_{err}^2$ has been corrected in accordance with the \textit{prior} distribution and the physical sense. It does not mean that calibration with the model $\mathcal{M}_1$ is incorrect, it only means that this model miss a substantial variance term due to a structural error in the experimental data. This term is the discrepancy and if one wants to be consistent with physics, one should consider the model $\mathcal{M}_3$ in this case. Note that with the model $\mathcal{M}_2$ the variance of the measurement error decreases without the add of the discrepancy. It may be due to the fact that the Gaussian process that emulates the code creates a compensation that takes into account a part of the discrepancy. \newline

@@

The use of a Gaussian process as a surrogate of the code (in the models $\mathcal{M}_2$ and $\mathcal{M}_4$) has to be manipulated with caution. Most of industrial codes are time consuming and the use of small DOE is required. However, if the surrogate does not represent well enough the numerical code, calibration will fail to retrieve a physical sense for the parameter. A shift of the \textit{posterior} density compared to the \textit{prior} density appears and calibration cannot be interpreted properly. A criterion can be introduced that can be seen as a recommendation upstream calibration\hc the $Q2$ of the surrogate has to be higher than $0.8$ to access proper calibration. Even with a $Q2>0.8$, calibration can lead to really wide \textit{posterior} densities which is the case in Figure \ref{fig:comparisionDensities1} for $\mathcal{M}_2$ and $\mathcal{M}_4$ ($Q2=0.826$ for the surrogate in $\mathcal{M}_2$ and $Q2=0.901$ for $\mathcal{M}_4$). This small decrease of variance \textit{a posteriori} might be unsatisfactory for the industrial company. An improvement of the Gaussian process can be brought by adding a small number of well chosen points in the original DOE. A methodology, called sequential design and developed in \citet{damblin2018},  is based on the EGO optimization to find new points regarding further calibration. From the original DOE of $50$ points used for previous calibrations (for $\mathcal{M}_2$ and $\mathcal{M}_4$) in Figure \ref{fig:comparisionDensities1}, $10$ points are appended to the original DOE by using the sequential design. Then calibration is performed on the new Gaussian process emulated with the new DOE and the results are displayed in Figure \ref{fig:calibrationSeq}. \newline

@@

@@

Figure \ref{fig:comparisionDensities2} illustrates the estimation of the parameters from the discrepancy term.
As expected, learning from data has improved our \textit{prior} belief by decreasing the \textit{prior} uncertainty of the parameters. 
It shows that in both cases (with and without surrogate) that the convergence seems to be reached at some point. \newline

@@

& $\mathcal{M}_1$ & $\mathcal{M}_2$ & $\mathcal{M}_3$ & $\mathcal{M}_4$ & $\mathcal{M}_2'$&  $\mathcal{M}_4'$ \\
\hline
\hline
coverage rate at 90\% (in \%) & 91 & 44 & 85 & 42 & 71 & 50 \\
\hline
RMSE of the instantaneous power ($W$) & 5.103 & 21.79 & 4.56 & 18.78 & 10.94 & 9.29 \\
\end{tabular}
\end{table}

The coverage rates for $\mathcal{M}_1$ and $\mathcal{M}_3$ corresponds to the chosen credibility level.
However for $\mathcal{M}_2$ and $\mathcal{M}_4$ the coverage rates are below this level. As expected the coverage rates of $\mathcal{M}_2'$ and $\mathcal{M}_4'$ increase since the quality of the surrogate has been improved. \newline

@@
